%====================
% EXPERIENCE A
%====================
\subsection{\texorpdfstring{Sr. iOS Developer \hfill Feb 2021 - Present}{Sr. iOS Developer (Feb 2021 - Present)}}
\subtext{4TYSIX App Labs \hfill Ahmedabad, India}
\begin{zitemize}
    \item Owned the full development lifecycle for 6+ iOS apps in a fast-paced environment, from initial scoping and architecture to shipping bi-weekly feature updates.
    \item Successfully collaborated in cross-functional teams (7+ members) in hybrid and fully remote settings, utilizing asynchronous
communication tools and practices ensuring project alignment and timely delivery.
    \item Operated autonomously to manage and deliver complex solo projects, taking complete end-to-end ownership from concept to launch, thriving in an ambiguous environment.
    \item Demonstrated high user empathy by shipping critical performance optimizations that led to a 30\% user retention boost, focusing on creating a delightful user experience.
    \item Managed app development for a portfolio of 8 apps with a combined user base of 500,000.
    \item Managed dependencies and modularized projects using Swift Package Manager (SPM).
    \item Utilized modern Swift concurrency features like async/await and actors to improve background processing and UI responsiveness.
\end{zitemize}

%====================
% EXPERIENCE B
%====================
\subsection{\texorpdfstring{iOS Developer \hfill Jan 2020 - Jan 2021}{iOS Developer}}
\subtext{4TYSIX App Labs \hfill Ahmedabad, India}
\begin{zitemize}
    \item Enhanced code efficiency in 5 production iOS applications, achieving a 30\% performance increase by optimizing data structures,
refactoring critical algorithms.
    \item Collaborated with designers and backend developers to implement new features.
    \item Utilized UIKit, Core Graphics, and other frameworks to create user-friendly interfaces.
    \item Published several apps, contributing to the company’s portfolio.
\end{zitemize}

%====================
% EXPERIENCE C
%====================
\subsection{\texorpdfstring{Jr. iOS Developer \hfill Feb 2018 - Jan 2020}{Jr. iOS Developer}}
\subtext{PROJECT CAFE TECHNOLOGIES \hfill Ahmedabad, India}
\begin{zitemize}
    \item Developed and maintained iOS applications with features like push notifications, offline mode, and real-time data synchronization.
    \item Contributed to the design and development of UI components following Apple’s Human Interface Guidelines.
    \item Debugged and resolved issues to improve app performance and stability, achieving a 25\% reduction in crash rate.
    \item Integrated third-party SDKs for features such as analytics, payment gateways, and social media login.
    \item Collaborated with cross-functional teams, including designers and backend developers, to deliver seamless user experiences.
\end{zitemize}

%====================
% EXPERIENCE E
%====================
%\subsection{{ROLE / PROJECT E \hfill MMM YYYY --- MMM YYYY}}
%\subtext{company E \hfill somewhere, state}
%\begin{zitemize}
%    \item In lobortis libero consectetur eros vehicula, vel pellentesque quam fringilla.
%    \item Ut malesuada purus at mi placerat dapibus.
%    \item Suspendisse finibus massa eu nisi dictum, a imperdiet tellus convallis.
%    \item Nam feugiat erat vestibulum lacus feugiat, efficitur gravida nunc imperdiet.
%    \item Morbi porta lacus vitae augue luctus, a rhoncus est sagittis.
%\end{zitemize}

%====================
% EXPERIENCE F
%====================
%\subsection{{ROLE / PROJECT F \hfill MMM YYYY --- MMM YYYY}}
%\subtext{company F \hfill somewhere, state}
%\begin{zitemize}
%    \item In lobortis libero consectetur eros vehicula, vel pellentesque quam fringilla.
%    \item Ut malesuada purus at mi placerat dapibus.
%    \item Ut malesuada purus at mi placerat dapibus.
%    \item Ut malesuada purus at mi placerat dapibus.
%\end{zitemize}

%====================
% EXPERIENCE G
%====================
%\subsection{{ROLE / PROJECT G \hfill MMM YYYY --- MMM YYYY}}
%\subtext{company G \hfill somewhere, state}
%\begin{zitemize}
%    \item In lobortis libero consectetur eros vehicula, vel pellentesque quam fringilla.
%    \item Ut malesuada purus at mi placerat dapibus.
%    \item Ut malesuada purus at mi placerat dapibus.
%    \item Ut malesuada purus at mi placerat dapibus.
%\end{zitemize}

%====================
% EXPERIENCE H
%====================
%\subsection{{ROLE / PROJECT H \hfill MMM YYYY --- MMM YYYY}}
%\subtext{company H \hfill somewhere, state}
%\begin{zitemize}
%    \item In lobortis libero consectetur eros vehicula, vel pellentesque quam fringilla.
%    \item Ut malesuada purus at mi placerat dapibus.
%    \item Ut malesuada purus at mi placerat dapibus.
%    \item Ut malesuada purus at mi placerat dapibus.
%\end{zitemize}

%====================
% EXPERIENCE I
%====================
%\subsection{{ROLE / PROJECT I \hfill MMM YYYY --- MMM YYYY}}
%\subtext{company I \hfill somewhere, state}
%\begin{zitemize}
%    \item In lobortis libero consectetur eros vehicula, vel pellentesque quam fringilla.
%    \item Ut malesuada purus at mi placerat dapibus.
%    \item Ut malesuada purus at mi placerat dapibus.
%    \item Ut malesuada purus at mi placerat dapibus.
%\end{zitemize}