% ====================
% PROJECT: ML Demo
% ====================
\noindent
{\color{highlight} \textbf{\large Apple ML Model Integration — Personal Demo}} \\
Explored Apple's on-device machine learning capabilities by integrating an Apple-provided ML model into a prototype iOS application. Built a SwiftUI interface to surface model outputs in real time, gaining hands-on familiarity with the end-to-end workflow of embedding ML into user-facing iOS experiences.
\vspace{1em}

% ====================
% PROJECT: Asianparent
% ====================
\noindent
{\color{highlight} \textbf{\large Asianparent: Pregnancy + Baby}} \\
\url{https://apps.apple.com/in/app/asianparent-pregnancy-baby/id1042523855} \\
Parenting community app architected with MVVM and SwiftUI for seamless declarative UI. Features real-time content feeds, CoreData-backed offline caching, and push notifications for pregnancy \& child development tracking.
\vspace{1em}

% ====================
% PROJECT: My Endless Book
% ====================
\noindent
{\color{highlight} \textbf{\large My Endless Book}} \\
\url{https://apps.apple.com/us/app/my-endless-book/id6480507474} \\
Collaborative writing platform built on Clean Architecture. Custom UI components for rich text editing, co-authoring, PDF/audiobook exports, and a fully customisable reading experience.
\vspace{1em}

% ====================
% PROJECT: Pepsi DRC
% ====================
\noindent
{\color{highlight} \textbf{\large Pepsi DRC}} \\
\url{https://apps.apple.com/in/app/pepsidrc/id1532856157} \\
Official online ordering app for Dubai Refreshment, structured using VIPER for complex routing and data flows. Features category browsing, real-time inventory, and doorstep delivery.
\vspace{1em}

% ====================
% PROJECT: BeeInvites
% ====================
\noindent
{\color{highlight} \textbf{\large BeeInvites}} \\
\url{https://apps.apple.com/gb/app/vuepay/id1454657419} \\
Event invitation platform using a custom keyboard extension, leveraging MVVM to manage complex UI states and SwiftUI animations. Includes Apple In-App Purchase subscription integration.
\vspace{1em}

% ====================
% PROJECT: SavvyCV4
% ====================
\noindent
{\color{highlight} \textbf{\large SavvyCV4}} \\
\url{https://apps.apple.com/in/app/savvycv4/id1632194198} \\
Bluetooth-connected levelling app using BLE and MVC. Delivers real-time $\pm 0.1^{\circ}$ precision sensor data with custom Core Graphics graphical display and persistent settings.
